Reinforcement Learning Based Transmitter-Receiver Selection for Distributed MIMO Radars

### 2020-01-17 paper.tex
Fix minor typo and modify TODO list

Performance in target detection and target localization depend on the SINR level \cite{aittomaki1, aittomaki2, antenna_subset_selection, selection_and_placement}.
Therefore, a reward function for reinforcement learning is proposed that depends on vector $\vsinrexp$ that consists of all the SINR values $\esinrexp$.
The following reward function is used for the employed MAB learning
\begin{equation}\label{eq:reward_func}
    r(\vasvrx, \vasvtx | \vsinrexp) = \frac{1}{N_S M_S}\sum_{n=1}^N \sum_{m=1}^M  \easvrx \easvtx \esinrexp,
\end{equation}
which is a mean of SINR values for the selected channels on a linear scale.
Furthermore, the reward maximization problem can be formulated as
\begin{equation}\label{eq:obj_func}
    \begin{array}{ll}
                &   \max_{\vasvrx, \vasvtx} r(\vasvrx, \vasvtx | \vsinrexp) \\[7pt]
    \text{s.t.} &   
                \left\{\begin{array}{l}
                    \sum_{n=1}^N \easvrx = N_S \\
                    \sum_{m=1}^M \easvtx = M_S.
                \end{array}\right.
    \end{array}
\end{equation}
It is possible to find an optimal solution for the equation (\ref{eq:obj_func}) if $\vsinrexp$ is known.
However, $\vsinrexp$ is not known since we can only obtain the measurements $\esp$. 
Furthermore, it might not be possible to probe all the channels at the same time.
Therefore, $\vsinrexp$ needs to be estimated from the received signal. 
By probing the different channels, an estimate $\vsinrb$ of the channel SINR values can be formed.
An approximate solution for the objective (\ref{eq:obj_func}) is found when the estimate $\vsinrb$ is used to condition the reward function (\ref{eq:reward_func}).
Different subsets must be explored sufficiently large number of times to reinforce the estimate $\vsinrb$ to identify the subset of TX-RX pairs yielding the highest SINR values.

>>>>

Performance in target detection and target localization depend on the SINR level \cite{aittomaki1, aittomaki2, antenna_subset_selection, selection_and_placement}.
Therefore, a reward function for reinforcement learning is proposed that depends on the vector $\vsinrexp$ that consists of all the SINR values $\esinrexp$.
The following reward function is used for the employed MAB learning
\begin{equation}\label{eq:reward_func}
    r(\vasvrx, \vasvtx | \vsinrexp) = \frac{1}{N_S M_S}\sum_{n=1}^N \sum_{m=1}^M  \easvrx \easvtx \esinrexp,
\end{equation}
which is a mean of SINR values for the selected channels on a linear scale.
Furthermore, the reward maximization problem can be formulated as
\begin{equation}\label{eq:obj_func}
    \begin{array}{ll}
                &   \max_{\vasvrx, \vasvtx} r(\vasvrx, \vasvtx | \vsinrexp) \\[7pt]
    \text{s.t.} &   
                \left\{\begin{array}{l}
                    \sum_{n=1}^N \easvrx = N_S \\
                    \sum_{m=1}^M \easvtx = M_S.
                \end{array}\right.
    \end{array}
\end{equation}
It is possible to find an optimal solution for the equation (\ref{eq:obj_func}) if $\vsinrexp$ is known.
However, $\vsinrexp$ is not known since we can only obtain the measurements $\esp$. 
Furthermore, it might not be possible to probe all the channels at the same time.
Therefore, $\vsinrexp$ needs to be estimated from the received signal. 
By probing the different channels, an estimate $\vsinrb$ of the channel SINR values can be formed.
An approximate solution for the objective (\ref{eq:obj_func}) is found when the estimate $\vsinrb$ is used to condition the reward function (\ref{eq:reward_func}).
Different subsets must be explored sufficiently large number of times to reinforce the estimate $\vsinrb$ to identify the subset of TX-RX pairs yielding the highest SINR values.
